---
title: "AI Return Nowcaster - SDF Price Range"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install & load package "httr" to access API later
if (!require("httr", quietly = TRUE)) {
  install.packages("httr")
}

Sys.setenv(TZ = "GMT")

```

## Introduction

This document explains how to use the AI Return Nowcaster **Stochastic Discount Factor (SDF) Price Range** endpoint of the **Private Equity Model API** provided by [prettymodels.ai](https://prettymodels.ai).
Our SDF price range endpoint combines the publications of

- [Driessen, Lin, Phalippou (2012)](https://doi.org/10.1017/S0022109012000221)
- [Ang, Chen, Goetzmann, Phalippou (2018)](https://doi.org/10.1111/jofi.12688)
- [Brown, Ghysels, Gredil (2023)](https://doi.org/10.1093/rfs/hhac045)

## Set API Base URL & API keys

```{r API base url and API keys}
base_product_url <- "https://base-product-url.app"
primary_api_key <- "needed-for-authentication"
secondary_api_key <- "needed-for-authentication"

```

```{r use Master Base URL, echo=FALSE}

# this is not relevant for API users!
file_name <- "api_root.R"
  
if (file.exists(file_name)) {
source(file_name)
  }

```

## Get fund segments and macro environments

```{r API get fund segments and macro environments}

post_request <- httr::GET(url = paste0(base_product_url, "common/fund_segments"))
fund_segments <- unlist(content(post_request, "parsed"))
# print(fund_segments)
post_request <- httr::GET(url = paste0(base_product_url, "common/macro_environments"))
macro_environments <- unlist(content(post_request, "parsed"))
# print(macro_environments)

```

## Define the API request body

Specify your input parameters in the request body:

- **fund_segment**: choose from [`r fund_segments`]
- **macro_environment**: choose from [`r macro_environments`]
- **rf_rate**: risk-free rate (0.01 corresponds to 1% risk-free rate p.a.)
- **list_input**: list of dicts containing the cash flows you want to price [{"cash_flow_amount": 100, "exit_time": 1}, {"cash_flow_amount": 50, "exit_time": 2}, ...]

**Please enter your own parameter assumptions!**

```{r API request bodies}

# Define the request body

request_body <- list(
  list_input = list(
    list(cash_flow_amount=100, exit_time=1), # example cash flow stream
    list(cash_flow_amount=150, exit_time=2), # example cash flow stream
    list(cash_flow_amount=220, exit_time=3) # example cash flow stream
  ),
  fund_segment= fund_segments[1],
  macro_environment= macro_environments[1],
  rf_rate= 0
)

```

## Send endpoint request

This endpoint provides a short-term return nowcast for a portfolio of private capital funds.

```{r send endpoint request}

# Select endpoint
endpoint <- "air_nowcaster/sdf_price_range"

# Build API URL
api_url <- paste0(base_product_url, endpoint)

# Create the POST request
post_request <- httr::POST(api_url,
                           add_headers(.headers = c("X-BLOBR-KEY" = primary_api_key)),
                           body = request_body,
                           encode = "json")
# print(post_request)


# Send the POST Request:
response <- httr::content(post_request, "parsed")
# print(response)

# Convert to data.frame
df <- data.frame(lapply(response, unlist))

# Plot data.fame containing results

  # Define mean and standard deviation
  m <- df$price_mean  # Mean
  s <- df$price_stdv  # Standard deviation
  
  # Generate x-values for the plot
  x <- seq(m - 4 * s, m + 4 * s, length = 1000)
  
  # Calculate the PDF values for the given mean and standard deviation
  pdf_values <- dnorm(x, mean = m, sd = s)
  
  # Create the plot
  plot(x, pdf_values, type = "l", col = "blue", lwd = 2,
       xlab = "Fund Price (discounted cash flows)", 
       ylab = "PDF", main = "Fund Price Range")
  abline(h=0, col="grey")
  abline(v=m, col="green", lwd=2)
  legend("topright", bty="n", legend = "expected price", col="green", lwd=2, lty=1)


```


